A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-07 paper/paper.tex
Even more gratuitous plotting

@@

>>>>

\paragraph{Vertex labels but no edge labels, undirected} are in \cref{figure:33v-cumulative}, and are not in other papers so we should omit this unless we see something interesting.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33v-cumulative.pdf}
    \caption{MCS 33\% vertex labelled, no edge labels, undirected instances, cumulative runtimes}\label{figure:33v-cumulative}
\end{figure}
